School Socioeconomic Status Context and Social Skills in Children

### 2020-11-02 manuscript.tex
Add supp material
Did the following:

* Added `supplementary_materials.Rmd`
* Modified function to produce full model outputs
* Added function to knit both manuscript and supp materials
* Updated pipeline with new functions
* Removed all old versions of codebook that have names in them

Should close #5

\begin{figure}
\centering
\includegraphics{/Users/philipparker/Dropbox/Projects_Research/CURRENT_WORKING/social_skills_2020/fig/flow.pdf}
\caption{\label{fig:consort}Participant flow diagramme}
\end{figure}

@@

Parents and teachers had moderate agreement for children at age 8 with correlations ranging from \emph{r} = 0.41 95\% CI{[}0.38, 0.43{]} for peer and \emph{r} = 0.4 95\% CI{[}0.37, 0.42{]} for conduct problems to \emph{r} = 0.29 95\% CI{[}0.26, 0.31{]} for prosocial behavior.

@@

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{llrrr}
\caption*{
\large Table 1\\ 
\small Effect of School Average SES on Social Skills\\ 
} \\ 
\toprule
Outcome & Report Source & Estimate & -95\% CI & +95\% CI \\ 
\midrule
conduct & teacher & $-0.152$ & $-0.261$ & $-0.046$ \\ 
social & teacher & $0.147$ & $0.056$ & $0.241$ \\ 
peer & teacher & $-0.115$ & $-0.204$ & $-0.024$ \\ 
conduct & parent & $-0.107$ & $-0.169$ & $-0.045$ \\ 
social & parent & $0.087$ & $0.018$ & $0.156$ \\ 
peer & parent & $-0.135$ & $-0.205$ & $-0.063$ \\ 
\bottomrule
\end{longtable}

@@

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{lllrrr}
\caption*{
\large Table 2\\ 
\small Effect of School Average SES by Student SES on Social Skills\\ 
} \\ 
\toprule
Outcome & Report Source & term & Estimate & -95\% CI & +95\% CI \\ 
\midrule
conduct & teacher & School Average SES & $-0.160$ & $-0.270$ & $-0.053$ \\ 
conduct & teacher & School Average SES by Student SES & $0.151$ & $0.064$ & $0.240$ \\ 
social & teacher & School Average SES & $0.156$ & $0.059$ & $0.252$ \\ 
social & teacher & School Average SES by Student SES & $-0.094$ & $-0.172$ & $-0.017$ \\ 
peer & teacher & School Average SES & $-0.126$ & $-0.216$ & $-0.036$ \\ 
peer & teacher & School Average SES by Student SES & $0.117$ & $0.044$ & $0.191$ \\ 
conduct & parent & School Average SES & $-0.112$ & $-0.175$ & $-0.048$ \\ 
conduct & parent & School Average SES by Student SES & $0.058$ & $0.006$ & $0.111$ \\ 
social & parent & School Average SES & $0.090$ & $0.020$ & $0.160$ \\ 
social & parent & School Average SES by Student SES & $-0.031$ & $-0.087$ & $0.027$ \\ 
peer & parent & School Average SES & $-0.144$ & $-0.217$ & $-0.074$ \\ 
peer & parent & School Average SES by Student SES & $0.117$ & $0.058$ & $0.176$ \\ 
\bottomrule
\end{longtable}

>>>>

\begin{figure}
\centering
\includegraphics{/Users/tasanders/GitHub/social_skills_2020/fig/flow.pdf}
\caption{\label{fig:consort}Participant flow diagramme}
\end{figure}

@@

Parents and teachers had moderate agreement for children at age 8 with correlations ranging from \emph{r} = 0.41 95\% CI{[}0.38, 0.43{]} for peer and \emph{r} = 0.39 95\% CI{[}0.37, 0.42{]} for conduct problems to \emph{r} = 0.29 95\% CI{[}0.26, 0.31{]} for prosocial behavior.

@@

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{llrrr}
\caption*{
\large Table 1\\ 
\small Effect of School Average SES on Social Skills\\ 
} \\ 
\toprule
Outcome & Report Source & Estimate & -95\% CI & +95\% CI \\ 
\midrule
conduct & teacher & $-0.154$ & $-0.264$ & $-0.043$ \\ 
social & teacher & $0.148$ & $0.054$ & $0.242$ \\ 
peer & teacher & $-0.116$ & $-0.204$ & $-0.029$ \\ 
conduct & parent & $-0.108$ & $-0.170$ & $-0.046$ \\ 
social & parent & $0.087$ & $0.018$ & $0.155$ \\ 
peer & parent & $-0.134$ & $-0.203$ & $-0.063$ \\ 
\bottomrule
\end{longtable}

@@

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{lllrrr}
\caption*{
\large Table 2\\ 
\small Effect of School Average SES by Student SES on Social Skills\\ 
} \\ 
\toprule
Outcome & Report Source & term & Estimate & -95\% CI & +95\% CI \\ 
\midrule
conduct & teacher & School Average SES & $-0.161$ & $-0.268$ & $-0.054$ \\ 
conduct & teacher & School Average SES by Student SES & $0.150$ & $0.063$ & $0.240$ \\ 
social & teacher & School Average SES & $0.157$ & $0.063$ & $0.250$ \\ 
social & teacher & School Average SES by Student SES & $-0.095$ & $-0.172$ & $-0.020$ \\ 
peer & teacher & School Average SES & $-0.126$ & $-0.218$ & $-0.035$ \\ 
peer & teacher & School Average SES by Student SES & $0.116$ & $0.046$ & $0.189$ \\ 
conduct & parent & School Average SES & $-0.112$ & $-0.176$ & $-0.047$ \\ 
conduct & parent & School Average SES by Student SES & $0.058$ & $0.006$ & $0.110$ \\ 
social & parent & School Average SES & $0.090$ & $0.023$ & $0.157$ \\ 
social & parent & School Average SES by Student SES & $-0.031$ & $-0.087$ & $0.029$ \\ 
peer & parent & School Average SES & $-0.143$ & $-0.213$ & $-0.074$ \\ 
peer & parent & School Average SES by Student SES & $0.117$ & $0.057$ & $0.179$ \\ 
\bottomrule
\end{longtable}
